Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Small tweak to crqa results

A permutation test for the CRQA of social cohesion and count of positive events
found no statistically significant difference for any of the metrics other than
TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistically significant difference for DET, NRLINE, L, ENTR, LAM, and
TT. All other metrics did not reach significance (Figure
\@ref(fig:plot-rp-targ-neg); \autoref{table-1}).

>>>>

A permutation test for the CRQA of social cohesion and count of positive events
found no statistically significant difference from chance for any of the metrics
other than TT (Figure \@ref(fig:plot-rp-targ-pos); \autoref{table-1}).

A permutation test for the CRQA of social cohesion and count of negative events
found a statistically significant difference from chance for DET, NRLINE, L,
ENTR, LAM, and TT. All other metrics did not reach significance (Figure
\@ref(fig:plot-rp-targ-neg); \autoref{table-1}).
